Spin canonical rings of log stacky curves

### 2015-07-14 curves-write-up/spin-cring.tex
moved some admissibility

\newcommand\ssec{\subsection}
\newcommand\BH{{\mathbb H}}
\newcommand\BN{{\mathbb N}}
\newcommand\BC{{\mathbb C}}
\newcommand\BR{{\mathbb R}}
\newcommand\BQ{{\mathbb Q}}
\newcommand\BP{{\mathbb P}}
\newcommand\BZ{{\mathbb Z}}
\newcommand\Bk{{\Bbbk}}

@@

@@

\begin{lem}
\label{lem:relations_from_generators_induction} 
Suppose $\halfcan$, $\halfcan' \in \BQ$ $\otimes$ $\di X$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, such that $R_{\halfcan'}$ generated by $x_1, \ldots, x_m$
and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over 
$R_{\halfcan'}$.  Let $I'$ and $I$ be the ideals relations of $\phi':\Bk[x_1, \ldots, x_m]\to R_{\halfcan'}$ and $\phi:\Bk[x_1, \ldots, x_m, y_1, \ldots y_n]\to R_{\halfcan}$ respectively.
Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and a monomial ordering $\prec$ such 
\begin{enumerate}
\item $S$ forms a $\Bk$-basis for $R_\halfcan$ over $R_\halfcan'$
\item $T \succ S\succ \Bk[x_1, \ldots, x_n]$ {\rm(}meaning all monomials in $T$ are bigger than all monomials in $S$ which are bigger than all monomials in $\Bk[x_1, \ldots, x_n]${\rm)}
\item All monomials in $\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
\begin{align*}
	S \; \cup\; \langle T\rangle \; \cup \; \initial(I') \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; \Bk[x_1, \ldots, x_m]
\end{align*}
\end{enumerate}
Then,
\begin{align*}
	\initial(I) & = \initial(I') \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n]
	+ \langle T \rangle.
\end{align*}
\end{lem}
\begin{proof}
First, notice that $I'\subseteq I$ so 
\[
	\initial(I)\supseteq \initial(I')\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n].
\]

@@

One key difference between the notion of admissibility in Definition ~\ref{defn:admissible} and that of Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky} is that
we cannot assume that $\{P_i\} \cap \Supp(\halfcan_X') = \emptyset$, as $H^0(X, \halfcan_X')$ may have no global sections. We circumvent this issue by working with the orders of zeros and poles relative to $\halfcan_X'$, rather than relative to the $\sco_X$.

\begin{defn}
\label{def:order-sup}
Let $D \in \di \sx.$ If $z$ is a rational section of $\sco(D)$ denote the order of
zero of $z$ at $P$ by $\ord_P^D(z)$.
\end{defn}

@@

The cases that $L' = 0, \: L' = P-Q +\frac{1}{3}P_1 + \frac{1}{3}P_2,$ and $L' = P-Q + \frac{2}{5}P_1$ were checked in Examples ~\ref{eg:base-1-0}, \ref{eg:base-1-33}, and \ref{eg:exception-1-5} respectively.

>>>>

\newcommand\ssec{\subsection}
\newcommand\sssec{\subsubsection}
\newcommand\BH{{\mathbb H}}
\newcommand\BN{{\mathbb N}}
\newcommand\BC{{\mathbb C}}
\newcommand\BR{{\mathbb R}}
\newcommand\BQ{{\mathbb Q}}
\newcommand\BP{{\mathbb P}}
\newcommand\BZ{{\mathbb Z}}
\newcommand\Bk{{\Bbbk}}

@@

\begin{defn}
\label{defn:order-sup}
Let $D \in \di \sx.$ If $z$ is a rational section of $\sco(D)$ denote the order of
zero of $z$ at $P$ by $\ord_P^D(z)$.
\end{defn}

@@

\begin{lem}
\label{lem:relations_from_generators_induction} 
Suppose $\halfcan$, $\halfcan' \in \BQ$ $\otimes$ $\di X$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, such that $R_{\halfcan'}$ generated by $x_1, \ldots, x_m$
and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over 
$R_{\halfcan'}$.  Let $I'$ and $I$ be the ideals relations of $\phi':\Bk[x_1, \ldots, x_m]\to R_{\halfcan'}$ and $\phi:\Bk[x_1, \ldots, x_m, y_1, \ldots y_n]\to R_{\halfcan}$ respectively.
Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and a monomial ordering $\prec$ such 
\begin{enumerate}
\item $S$ forms a $\Bk$-basis for $R_\halfcan$ over $R_\halfcan'$
\item $T \succ S\succ \Bk[x_1, \ldots, x_n]$ {\rm(}meaning all monomials in $T$ are bigger than all monomials in $S$ which are bigger than all monomials in $\Bk[x_1, \ldots, x_n]${\rm)}
\item All monomials in $\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
\begin{align*}
	S \; \cup\; \langle T\rangle \; \cup \; \initial(I') \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; \Bk[x_1, \ldots, x_m]
\end{align*}
\end{enumerate}
Then,
\begin{align*}
	\initial(I) & = \initial(I') \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n]
	+ \langle T \rangle.
\end{align*}
\end{lem}

\sssec*{Idea of Proof:} To get $\supseteq$, we use the fact that

\begin{proof}
First, notice that $I'\subseteq I$ so 
\[
	\initial(I)\supseteq \initial(I')\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n].
\]

@@

One key difference between the notion of admissibility in Definition ~\ref{defn:admissible} and that of Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky} is that
we cannot assume that $\{P_i\} \cap \Supp(\halfcan_X') = \emptyset$, as $H^0(X, \halfcan_X')$ may have no global sections. We circumvent this issue by working with the orders of zeros and poles relative to $\halfcan_X'$, rather than relative to the $\sco_X,$ using Definition ~\ref{defn:order-sup}.

@@

Generators and relations $L' = 0, \: L' = P-Q +\frac{1}{3}P_1 + \frac{1}{3}P_2,$ and $L' = P-Q + \frac{2}{5}P_1$ were checked in Examples ~\ref{eg:base-1-0}, \ref{eg:base-1-33}, and \ref{eg:exception-1-5} respectively. Note that admissibility for $L' = P-Q +\frac{1}{3}P_1 + \frac{1}{3}P_2,$ is verified in Example ~\ref{eg:base-1-33-adm}. The verification of admissibility for the other cases is similar.
